Abstract Data Type Inference

### 2015-03-24 intro.tex
Quick typo fixes.

The contributions and outline of this work are as follows:
\begin{itemize}

@@

\end{itemize}
We conclude with a discussion of the limitations of our approach
(§\ref{sec:discussion}) and related work (§\ref{sec:related}).

>>>>

In summary, the contributions and outline of this work are:
\begin{itemize}

@@

\end{itemize}
We conclude with a discussion about the limitations of our approach
(§\ref{sec:discussion}) and related work (§\ref{sec:related}).
